Estimating Planetary Habitability via Particle Swarm Optimization of CES Production Functions.

### 2018-01-17 docs/report/draft.tex
Added option for specifying DPI.
Changed iter plot colors.
Added the plots to draft.tex
Finished results.

\documentclass[10pt]{article}

@@

\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{mathtools}
\usepackage{bm}
\usepackage{siunitx}

\sisetup{output-exponent-marker=\ensuremath{\mathrm{e}}}

@@

This paper demonstrates the applicability of \pso\ in estimating CDHS and CEESA scores of an exoplanet by maximizing
their respective production functions, discussed in Sections~\ref{subsec:cdhs} and~\ref{subsec:ceesa}. CDHS considers
the planet's Radius, Mass, Escape Velocity and Surface Temperature, while CEESA includes a fifth parameter, the Orbital
Eccentricity of the planet. The Exoplanets Catalog hosted by the Planetary Habitability Laboratory, UPR Arecibo records
these parameters for each exoplanet in Earth Units. Section~\ref{sec:results} reports the performance of PSO and
contrasts it against an earlier effort to estimate these scores using Stochastic Gradient Ascent (SGA).

\section{Habitability Scores}
% Add the citations to Saha's papers.

@@

\section{Experiment and Results}

The data set used for analysis is the Confirmed Exoplanets Catalog maintained by the Planetary Habitability Laboratory
(PHL). The catalog records observed and modeled parameters for exoplanets confirmed by the Extrasolar Planets
Encyclopedia. Table~\ref{tab:param} describes the parameters from the PHL Exoplanets Catalog (PHL-EC) used for the
experiment. Since surface temperature and eccentricity are not recorded in Earth Units, we normalized these values by
dividing them with Earth's surface temperature (288K) and eccentricity (0.017). PHL-EC assumes an Eccentricity of 0 when
unavailable.

\begin{table}
  \begin{center}
    \begin{tabular}{l l l}
      \toprule
      \textbf{Parameter} & \textbf{Description} & \textbf{Unit}\\
      \midrule
      P. Radius       & Estimated radius      & Earth Units (EU)\\
      P. Density      & Density               & Earth Units (EU)\\
      P. Esc Vel      & Escape velocity       & Earth Units (EU)\\
      P. Ts Mean      & Surface temperature   & Kelvin (K)\\
      P. Eccentricity & Orbital eccentricity\\
      \bottomrule
    \end{tabular}
  \end{center}
  \caption{Parameters from the PHL-EC used for the experiment.}\label{tab:param}
\end{table}

The implemenation uses $n=25$ particles to traverse the search space with learning rates of $\lambda_g=0.8$ and
$\lambda_p=0.2$. Velocity is regulated through a friction coefficient of $\mu=0.6$ and bound by $\pm1.0$. We have used
an error threshold of $\epsilon=\num{1e-6}$ in converting strict inequalities to non-strict inequalities, and a
tolerance of $\tau=\num{1e-7}$ when transforming an equality constraint to a pair of inequalities. Further
implementation details are discussed in Appendix~\ref{app:imp}.

Tables~\ref{tab:cdhscrs} and~\ref{tab:cdhsdrs} record the CDHS values for a sample of exoplanets under CRS and DRS
respectively at $w_i=0.99$ and $w_s=0.01$. Tables~\ref{tab:ceesacrs} and~\ref{tab:ceesadrs} record the same for the
CEESA scores. All tables also record the number of iterations taken to converge to a stable $\gbest$ value.

\begin{table}
  \centering
  \begin{tabular}{l r r r r r r r r r r}
    \toprule
    Name & Class & $\alpha$ & $\beta$ & $Y_i$ & $i_i$ & $\gamma$ & $\delta$ & $Y_s$ & $i_s$ & $\mathit{CDHS}$\\
    \midrule
    GJ 176 b & non & 0.460 & 0.540 & 1.90 & 50 & 0.107 & 0.893 & 2.11 & 61 & 1.90\\
    GJ 667 C b & non & 0.423 & 0.577 & 1.71 & 58 & 0.692 & 0.308 & 1.81 & 54 & 1.71\\
    GJ 667 C e & psy & 0.129 & 0.871 & 1.40 & 50 & 0.258 & 0.742 & 1.39 & 55 & 1.40\\
    GJ 667 C f & psy & 0.534 & 0.466 & 1.40 & 48 & 0.865 & 0.135 & 1.39 & 47 & 1.40\\
    GJ 3634 b & non & 0.409 & 0.591 & 1.89 & 58 & 0.724 & 0.276 & 2.09 & 48 & 1.89\\
    HD 20794 c & non & 0.260 & 0.740 & 1.35 & 50 & 0.096 & 0.904 & 1.34 & 58 & 1.35\\
    HD 40307 e & non & 0.168 & 0.832 & 1.50 & 49 & 0.636 & 0.364 & 1.53 & 63 & 1.50\\
    HD 40307 f & non & 0.702 & 0.298 & 1.52 & 68 & 0.303 & 0.697 & 1.55 & 45 & 1.52\\
    HD 40307 g & psy & 0.964 & 0.036 & 1.82 & 51 & 0.083 & 0.917 & 1.98 & 55 & 1.82\\
    Kepler-186 f & hyp & 0.338 & 0.662 & 1.17 & 50 & 0.979 & 0.021 & 1.12 & 40 & 1.17\\
    Proxima Cen b & psy & 0.515 & 0.484 & 1.12 & 37 & 0.755 & 0.245 & 1.07 & 00 & 1.12\\
    TRAPPIST-1 b & non & 0.319 & 0.681 & 1.09 & 00 & 0.801 & 0.199 & 0.89 & 00 & 1.09\\
    TRAPPIST-1 c & non & 0.465 & 0.535 & 1.06 & 00 & 0.935 & 0.065 & 1.14 & 26 & 1.06\\
    TRAPPIST-1 d & mes & 0.635 & 0.365 & 0.77 & 34 & 0.475 & 0.525 & 0.73 & 47 & 0.77\\
    TRAPPIST-1 e & psy & 0.145 & 0.855 & 0.92 & 00 & 0.897 & 0.103 & 0.83 & 55 & 0.92\\
    TRAPPIST-1 g & hyp & 0.226 & 0.774 & 1.13 & 43 & 0.876 & 0.124 & 1.09 & 00 & 1.13\\
    \bottomrule
  \end{tabular}
  \caption{Estimated values of CDHS under CRS by PSO.\\
    \footnotesize $\alpha$, $\beta$, $\gamma$ and $\delta$ record the parameters of Equation~\ref{eq:cdhscrs}. $Y_i$
    and $Y_s$ record the maxima for the objective functions. $i_i$ and $i_s$ specify the number of iterations taken to
    converge to a stable $\gbest$ value. Under the Class column there are four categories for the planets ---
    Psychroplanets (psy), Mesoplanets (mes), Non-Habitable planets (non) and Hypopsychroplanets (hyp).  $\mathit{CDHS}$
    is the final scores with $w_i=0.99$ and $w_s=0.01$.
  }\label{tab:cdhscrs}
\end{table}

\begin{table}
  \centering
  \begin{tabular}{l r r r r r r r r r r}
    \toprule
    Name & Class & $\alpha$ & $\beta$ & $Y_i$ & $i_i$ & $\gamma$ & $\delta$ & $Y_s$ & $i_s$ & $\mathit{CDHS}$\\
    \midrule
    GJ 176 b & non & 0.395 & 0.604 & 1.90 & 059 & 0.372 & 0.627 & 2.11 & 056 & 1.90\\
    GJ 667 C b & non & 0.781 & 0.218 & 1.71 & 058 & 0.902 & 0.097 & 1.81 & 057 & 1.71\\
    GJ 667 C e & psy & 0.179 & 0.820 & 1.40 & 049 & 0.234 & 0.765 & 1.39 & 060 & 1.40\\
    GJ 667 C f & psy & 0.704 & 0.295 & 1.40 & 064 & 0.398 & 0.601 & 1.39 & 061 & 1.40\\
    GJ 3634 b & non & 0.602 & 0.397 & 1.89 & 059 & 0.429 & 0.570 & 2.09 & 077 & 1.89\\
    HD 20794 c & non & 0.014 & 0.985 & 1.35 & 050 & 0.116 & 0.883 & 1.34 & 045 & 1.35\\
    HD 40307 e & non & 0.752 & 0.247 & 1.50 & 060 & 0.677 & 0.322 & 1.53 & 050 & 1.50\\
    HD 40307 f & non & 0.887 & 0.112 & 1.52 & 051 & 0.261 & 0.738 & 1.55 & 060 & 1.52\\
    HD 40307 g & psy & 0.300 & 0.699 & 1.82 & 062 & 0.785 & 0.214 & 1.98 & 056 & 1.82\\
    Kepler-186 f & hyp & 0.073 & 0.926 & 1.17 & 046 & 0.740 & 0.259 & 1.12 & 051 & 1.17\\
    Proxima Cen b & psy & 0.045 & 0.954 & 1.12 & 057 & 0.216 & 0.783 & 1.07 & 053 & 1.12\\
    TRAPPIST-1 b & non & 0.102 & 0.897 & 1.09 & 041 & 0.000 & 0.000 & 1.00 & 065 & 1.09\\
    TRAPPIST-1 c & non & 0.471 & 0.528 & 1.06 & 044 & 0.227 & 0.772 & 1.14 & 057 & 1.06\\
    TRAPPIST-1 d & mes & 0.000 & 0.000 & 1.00 & 067 & 0.000 & 0.000 & 1.00 & 059 & 1.00\\
    TRAPPIST-1 e & psy & 0.000 & 0.000 & 1.00 & 055 & 0.000 & 0.000 & 1.00 & 057 & 1.00\\
    TRAPPIST-1 g & hyp & 0.888 & 0.111 & 1.13 & 047 & 0.949 & 0.050 & 1.09 & 046 & 1.13\\
    \bottomrule
  \end{tabular}
  \caption{Estimated values of CDHS under DRS by PSO.\\
    \footnotesize Here, $\alpha$, $\beta$, $\gamma$ and $\delta$ record the parameters of Equation~\ref{eq:cdhsdrs}. The
    other columns are the same as those in Table~\ref{tab:cdhscrs}.
  }\label{tab:cdhsdrs}
\end{table}

\begin{table}
  \centering
  \begin{tabular}{l r r r r r r r r r r}
    \toprule
    Name & Class & $r$ & $d$ & $t$ & $v$ & $e$ & $\rho$ & $\eta$ & $\mathit{CEESA}$ & $i$\\
    \midrule
    GJ 176 b & non & 0.304 & 0.001 & 0.375 & 0.271 & 0.050 & 0.467 & 0.808 & 1.52 &  85\\
    GJ 667 C b & non & 0.297 & 0.010 & 0.318 & 0.052 & 0.322 & 0.682 & 0.730 & 2.36 &  90\\
    GJ 667 C e & psy & 0.230 & 0.286 & 0.137 & 0.199 & 0.148 & 0.551 & 0.906 & 1.14 &  85\\
    GJ 667 C f & psy & 0.397 & 0.035 & 0.152 & 0.402 & 0.014 & 0.793 & 0.999 & 1.31 & 100\\
    GJ 3634 b & non & 0.178 & 0.175 & 0.005 & 0.194 & 0.447 & 0.894 & 0.657 & 2.07 &  94\\
    HD 20794 c & non & 0.073 & 0.142 & 0.452 & 0.190 & 0.144 & 0.953 & 0.635 & 1.20 &  78\\
    HD 40307 e & non & 0.156 & 0.307 & 0.185 & 0.033 & 0.319 & 0.428 & 0.939 & 2.69 &  88\\
    HD 40307 f & non & 0.272 & 0.231 & 0.064 & 0.305 & 0.127 & 0.676 & 0.802 & 1.28 &  77\\
    HD 40307 g & psy & 0.113 & 0.219 & 0.066 & 0.454 & 0.148 & 0.711 & 0.991 & 3.26 &  92\\
    Kepler-186 f & hyp & 0.039 & 0.159 & 0.116 & 0.329 & 0.357 & 0.253 & 0.919 & 1.35 &  70\\
    Proxima Cen b & psy & 0.272 & 0.173 & 0.284 & 0.193 & 0.079 & 0.615 & 0.114 & 0.99 &  75\\
    TRAPPIST-1 b & non & 0.488 & 0.151 & 0.039 & 0.193 & 0.129 & 0.151 & 0.014 & 0.99 &  87\\
    TRAPPIST-1 c & non & 0.172 & 0.236 & 0.275 & 0.242 & 0.075 & 0.969 & 0.962 & 1.06 &  80\\
    TRAPPIST-1 d & mes & 0.106 & 0.308 & 0.075 & 0.218 & 0.293 & 0.844 & 0.017 & 0.99 &  93\\
    TRAPPIST-1 e & psy & 0.189 & 0.266 & 0.192 & 0.094 & 0.260 & 0.371 & 0.006 & 0.99 &  84\\
    TRAPPIST-1 g & hyp & 0.326 & 0.186 & 0.143 & 0.278 & 0.067 & 0.315 & 0.021 & 1.00 &  76\\
    \bottomrule
  \end{tabular}
  \caption{Estimated values of CEESA under DRS by PSO.\\
    \footnotesize $r$, $d$, $t$, $v$, $e$, $\rho$ and $eta$ record the parameters of Equation~\ref{eq:ceesadrs}.
    $\mathit{CEESA}$ records the maxima of the objective function. $i$ specifies the number of iterations taken to
    converge to the maxima.
  }\label{tab:ceesadrs}
\end{table}

\begin{table}
  \centering
  \begin{tabular}{l r r r r r r r r r}
    \toprule
    Name & Class & $r$ & $d$ & $t$ & $v$ & $e$ & $\rho$ & $\mathit{CEESA}$ & $i$\\
    \midrule
    GJ 176 b & non & 0.194 & 0.020 & 0.315 & 0.465 & 0.006 & 0.398 & 1.88 &  86\\
    GJ 667 C b & non & 0.162 & 0.289 & 0.090 & 0.087 & 0.372 & 0.836 & 3.54 & 107\\
    GJ 667 C e & psy & 0.373 & 0.032 & 0.134 & 0.304 & 0.157 & 0.217 & 1.25 &  71\\
    GJ 667 C f & psy & 0.394 & 0.006 & 0.043 & 0.360 & 0.196 & 0.490 & 1.44 &  81\\
    GJ 3634 b & non & 0.351 & 0.122 & 0.006 & 0.069 & 0.453 & 0.439 & 2.89 &  96\\
    HD 20794 c & non & 0.101 & 0.077 & 0.691 & 0.071 & 0.059 & 0.756 & 1.58 &  94\\
    HD 40307 e & non & 0.069 & 0.091 & 0.097 & 0.173 & 0.569 & 0.768 & 5.29 &  94\\
    HD 40307 f & non & 0.285 & 0.161 & 0.053 & 0.443 & 0.058 & 0.342 & 1.42 &  73\\
    HD 40307 g & psy & 0.156 & 0.010 & 0.081 & 0.302 & 0.451 & 0.612 & 7.15 &  94\\
    Kepler-186 f & hyp & 0.036 & 0.017 & 0.082 & 0.383 & 0.483 & 0.929 & 1.68 &  85\\
    Proxima Cen b & psy & 0.352 & 0.383 & 0.103 & 0.059 & 0.103 & 0.936 & 0.89 &  83\\
    TRAPPIST-1 b & non & 0.148 & 0.147 & 0.344 & 0.269 & 0.093 & 0.767 & 0.94 &  81\\
    TRAPPIST-1 c & non & 0.038 & 0.060 & 0.575 & 0.321 & 0.005 & 0.602 & 1.17 &  86\\
    TRAPPIST-1 d & mes & 0.023 & 0.065 & 0.475 & 0.391 & 0.045 & 0.830 & 0.84 &  79\\
    TRAPPIST-1 e & psy & 0.176 & 0.464 & 0.253 & 0.103 & 0.004 & 0.920 & 0.86 &  81\\
    TRAPPIST-1 g & hyp & 0.060 & 0.086 & 0.310 & 0.540 & 0.004 & 0.848 & 0.97 &  86\\
    \bottomrule
  \end{tabular}
  \caption{Estimated values of CEESA under CRS by PSO.\\
    \footnotesize Here, $r$, $d$, $t$, $v$, $e$ and $\rho$ record the parameters of Equation~\ref{eq:ceesacrs}. Since
    under the CRS constraint $\eta=1$, there is no need for the parameter in the problem.
  }\label{tab:ceesacrs}
\end{table}

% \begin{pointers}
% \item The values and proximity to earth's habitability score.
% \item Values that do not converge. Or were hard to converge.
% \item Speed of convergence graphs.
% \item Graph1: Iterations to convergence vs. Number of particles.
% \item Graph2: Distribution of number of iterations to convergence.
% \item Graph3: Iterations to convergence vs. Constraint parameters.
% \end{pointers}

>>>>

\documentclass[9pt]{article}

@@

\usepackage{algorithm}
\usepackage{algpseudocode}

\usepackage{booktabs}
\usepackage{enumitem}

\usepackage{graphicx}
\usepackage{subcaption}

\usepackage{mathtools}
\usepackage{bm}
\usepackage{siunitx}

\graphicspath{{figs/}}
\sisetup{output-exponent-marker=\ensuremath{\mathrm{e}}}

@@

This paper demonstrates the applicability of \pso\ in estimating CDHS and CEESA scores of an exoplanet by maximizing
their respective production functions, discussed in Sections~\ref{subsec:cdhs} and~\ref{subsec:ceesa}. CDHS considers
the planet's Radius, Mass, Escape Velocity and Surface Temperature, while CEESA includes a fifth parameter, the Orbital
Eccentricity of the planet. The Exoplanets Catalog hosted by the Planetary Habitability Laboratory, UPR Arecibo records
these parameters for each exoplanet in Earth Units. Section~\ref{sec:results} reports the performance of PSO and
discusses the distribution of the habitability scores of the exoplanets.

\section{Habitability Scores}\label{sec:habscore}
% Add the citations to Saha's papers.

@@

\section{Experiment and Results}\label{sec:results}

The data set used for estimating the Habitability Scores of exoplanets, described in Section~\ref{sec:habscore}, was the
Confirmed Exoplanets Catalog maintained by the Planetary Habitability Laboratory (PHL). The catalog records observed and
modeled parameters for exoplanets confirmed by the Extrasolar Planets Encyclopedia. Table~\ref{tab:param} describes the
parameters from the PHL Exoplanets Catalog (PHL-EC) used for the experiment. Since surface temperature and eccentricity
are not recorded in Earth Units, we normalized these values by dividing them with Earth's surface temperature (288K) and
eccentricity (0.017). PHL-EC assumes an Eccentricity of 0 when unavailable. The PHL-EC records empty values for planets
whose surface temperature is not known. We chose to drop these records from the experiment.

\begin{table}
  \begin{center}
    \begin{tabular}{l l l}
      \toprule
      \textbf{Parameter} & \textbf{Description} & \textbf{Unit}\\
      \midrule
      P. Radius       & Estimated radius         & Earth Units (EU)\\
      P. Density      & Density                  & Earth Units (EU)\\
      P. Esc Vel      & Escape velocity          & Earth Units (EU)\\
      P. Ts Mean      & Mean Surface temperature & Kelvin (K)\\
      P. Eccentricity & Orbital eccentricity\\
      \bottomrule
    \end{tabular}
  \end{center}
  \caption{Parameters from the PHL-EC used for the experiment.}\label{tab:param}
\end{table}

Our implemenation used $n=25$ particles to traverse the search space, with learning rates $\lambda_g=0.8$ and
$\lambda_p=0.2$. It regulated velocity through a friction coefficient of $\mu=0.6$ and upper and lower bounds $\pm1.0$.
It used an error threshold of $\epsilon=\num{1e-6}$ to convert strict inequalities to non-strict inequalities, and a
tolerance of $\tau=\num{1e-7}$ to transform an equality constraint to a pair of inequalities. Further implementation
details are discussed in Appendix~\ref{app:imp}.

Tables~\ref{tab:cdhscrs} and~\ref{tab:cdhsdrs} record the CDHS values for a sample of exoplanets under CRS and DRS
respectively at $w_i=0.99$ and $w_s=0.01$. Tables~\ref{tab:ceesacrs} and~\ref{tab:ceesadrs} record the same for the
CEESA scores. All tables also record the number of iterations taken to converge to a stable $\gbest$ value. As seen in
the tables, although CEESA has 7 parameters and 16 constraints under DRS, PSO takes just over twice the number of
iterations to converge as in each step of CDHS, which has 2 parameters and 5 constraints. This is a promising result as
it indicates that the iterations required for converging increases sub-linearly with the number of parameters in the
model.

The plots in Figures~\ref{fig:distcdcrs} and~\ref{fig:distcddrs} indicate the distribution of the CDHS across the
exoplanets tested from the PHL-EC.\@ Figures~\ref{fig:itercdcrs} and~\ref{fig:itercddrs} show the distribution of
iterations required to converge to a global maxima. The spike at 0 is caused by particles converging to a $\gbest$ that
does not shift from the original position (for a more detailed explanation see Appendix \ref{app:con}). The plots in
Figures~\ref{fig:distcedrs} and~\ref{fig:distcedrs} indicate the distribution of the CEESA score across the exoplanets,
while Figures~\ref{fig:itercedrs} and~\ref{fig:itercecrs} indicate the distribution of iterations to convergence. These
graphs aggregate the results of optimizing the Habitability Production Functions (Equations~\ref{eq:cdhscrs},
~\ref{eq:cdhsdrs},~\ref{eq:ceesadrs} and~\ref{eq:ceesacrs}) for each exoplanet in the PHL-EC by the method described in
Algorithm~\ref{alg:cop}.

\begin{figure}
  \centering
  \begin{subfigure}[b]{0.4\textwidth}
    \includegraphics[width=\textwidth]{dcdhscrs.png}
    \caption{CRS Score Distribution}\label{fig:distcdcrs}
  \end{subfigure}
  \quad
  \begin{subfigure}[b]{0.4\textwidth}
    \includegraphics[width=\textwidth]{dcdhsdrs.png}
    \caption{DRS Score Distribution}\label{fig:distcddrs}
  \end{subfigure}

  \begin{subfigure}[b]{0.4\textwidth}
    \includegraphics[width=\textwidth]{icdhscrs.png}
    \caption{CRS Iterations Distribution}\label{fig:itercdcrs}
  \end{subfigure}
  \quad
  \begin{subfigure}[b]{0.4\textwidth}
    \includegraphics[width=\textwidth]{icdhsdrs.png}
    \caption{DRS Iterations Distribution}\label{fig:itercddrs}
  \end{subfigure}
  \caption{Plots for the Cobb-Douglas Habitability Score.}\label{fig:cdhs}
\end{figure}

\begin{figure}
  \centering
  \begin{subfigure}[b]{0.4\textwidth}
    \includegraphics[width=\textwidth]{dceesacrs.png}
    \caption{CRS Score Distribution}\label{fig:distcecrs}
  \end{subfigure}
  \quad
  \begin{subfigure}[b]{0.4\textwidth}
    \includegraphics[width=\textwidth]{dceesadrs.png}
    \caption{DRS Score Distribution}\label{fig:distcedrs}
  \end{subfigure}

  \begin{subfigure}[b]{0.4\textwidth}
    \includegraphics[width=\textwidth]{iceesacrs.png}
    \caption{CRS Iterations Distribution}\label{fig:itercecrs}
  \end{subfigure}
  \quad
  \begin{subfigure}[b]{0.4\textwidth}
    \includegraphics[width=\textwidth]{iceesadrs.png}
    \caption{DRS Iterations Distribution}\label{fig:itercedrs}
  \end{subfigure}
  \caption{Plots for the Constant Elasticity Earth Similarity Approach.}\label{fig:ceesa}
\end{figure}

\begin{table}
  \centering
  \begin{subtable}{\textwidth}
    \centering
    \begin{tabular}{l r r r r r r r r r r}
      \toprule
      Name & Class & $\alpha$ & $\beta$ & $Y_i$ & $i_i$ & $\gamma$ & $\delta$ & $Y_s$ & $i_s$ & $\mathit{CDHS}$\\
      \midrule
      GJ 176 b & non & 0.460 & 0.540 & 1.90 & 50 & 0.107 & 0.893 & 2.11 & 61 & 1.90\\
      GJ 667 C b & non & 0.423 & 0.577 & 1.71 & 58 & 0.692 & 0.308 & 1.81 & 54 & 1.71\\
      GJ 667 C e & psy & 0.129 & 0.871 & 1.40 & 50 & 0.258 & 0.742 & 1.39 & 55 & 1.40\\
      GJ 667 C f & psy & 0.534 & 0.466 & 1.40 & 48 & 0.865 & 0.135 & 1.39 & 47 & 1.40\\
      GJ 3634 b & non & 0.409 & 0.591 & 1.89 & 58 & 0.724 & 0.276 & 2.09 & 48 & 1.89\\
      HD 20794 c & non & 0.260 & 0.740 & 1.35 & 50 & 0.096 & 0.904 & 1.34 & 58 & 1.35\\
      HD 40307 e & non & 0.168 & 0.832 & 1.50 & 49 & 0.636 & 0.364 & 1.53 & 63 & 1.50\\
      HD 40307 f & non & 0.702 & 0.298 & 1.52 & 68 & 0.303 & 0.697 & 1.55 & 45 & 1.52\\
      HD 40307 g & psy & 0.964 & 0.036 & 1.82 & 51 & 0.083 & 0.917 & 1.98 & 55 & 1.82\\
      Kepler-186 f & hyp & 0.338 & 0.662 & 1.17 & 50 & 0.979 & 0.021 & 1.12 & 40 & 1.17\\
      Proxima Cen b & psy & 0.515 & 0.484 & 1.12 & 37 & 0.755 & 0.245 & 1.07 & 00 & 1.12\\
      TRAPPIST-1 b & non & 0.319 & 0.681 & 1.09 & 00 & 0.801 & 0.199 & 0.89 & 00 & 1.09\\
      TRAPPIST-1 c & non & 0.465 & 0.535 & 1.06 & 00 & 0.935 & 0.065 & 1.14 & 26 & 1.06\\
      TRAPPIST-1 d & mes & 0.635 & 0.365 & 0.77 & 34 & 0.475 & 0.525 & 0.73 & 47 & 0.77\\
      TRAPPIST-1 e & psy & 0.145 & 0.855 & 0.92 & 00 & 0.897 & 0.103 & 0.83 & 55 & 0.92\\
      TRAPPIST-1 g & hyp & 0.226 & 0.774 & 1.13 & 43 & 0.876 & 0.124 & 1.09 & 00 & 1.13\\
      \bottomrule
    \end{tabular}
    \caption{Estimated habitability scores under CRS.}\label{tab:cdhscrs}
  \end{subtable}

  \vspace{4em}

  \begin{subtable}{\textwidth}
    \centering
    \begin{tabular}{l r r r r r r r r r r}
      \toprule
      Name & Class & $\alpha$ & $\beta$ & $Y_i$ & $i_i$ & $\gamma$ & $\delta$ & $Y_s$ & $i_s$ & $\mathit{CDHS}$\\
      \midrule
      GJ 176 b & non & 0.395 & 0.604 & 1.90 & 59 & 0.372 & 0.627 & 2.11 & 56 & 1.90\\
      GJ 667 C b & non & 0.781 & 0.218 & 1.71 & 58 & 0.902 & 0.097 & 1.81 & 57 & 1.71\\
      GJ 667 C e & psy & 0.179 & 0.820 & 1.40 & 49 & 0.234 & 0.765 & 1.39 & 60 & 1.40\\
      GJ 667 C f & psy & 0.704 & 0.295 & 1.40 & 64 & 0.398 & 0.601 & 1.39 & 61 & 1.40\\
      GJ 3634 b & non & 0.602 & 0.397 & 1.89 & 59 & 0.429 & 0.570 & 2.09 & 77 & 1.89\\
      HD 20794 c & non & 0.014 & 0.985 & 1.35 & 50 & 0.116 & 0.883 & 1.34 & 45 & 1.35\\
      HD 40307 e & non & 0.752 & 0.247 & 1.50 & 60 & 0.677 & 0.322 & 1.53 & 50 & 1.50\\
      HD 40307 f & non & 0.887 & 0.112 & 1.52 & 51 & 0.261 & 0.738 & 1.55 & 60 & 1.52\\
      HD 40307 g & psy & 0.300 & 0.699 & 1.82 & 62 & 0.785 & 0.214 & 1.98 & 56 & 1.82\\
      Kepler-186 f & hyp & 0.073 & 0.926 & 1.17 & 46 & 0.740 & 0.259 & 1.12 & 51 & 1.17\\
      Proxima Cen b & psy & 0.045 & 0.954 & 1.12 & 57 & 0.216 & 0.783 & 1.07 & 53 & 1.12\\
      TRAPPIST-1 b & non & 0.102 & 0.897 & 1.09 & 41 & 0.000 & 0.000 & 1.00 & 65 & 1.09\\
      TRAPPIST-1 c & non & 0.471 & 0.528 & 1.06 & 44 & 0.227 & 0.772 & 1.14 & 57 & 1.06\\
      TRAPPIST-1 d & mes & 0.000 & 0.000 & 1.00 & 67 & 0.000 & 0.000 & 1.00 & 59 & 1.00\\
      TRAPPIST-1 e & psy & 0.000 & 0.000 & 1.00 & 55 & 0.000 & 0.000 & 1.00 & 57 & 1.00\\
      TRAPPIST-1 g & hyp & 0.888 & 0.111 & 1.13 & 47 & 0.949 & 0.050 & 1.09 & 46 & 1.13\\
      \bottomrule
    \end{tabular}
    \caption{Estimated habitability scores under DRS.}\label{tab:cdhsdrs}
  \end{subtable}
  \caption{Cobb-Douglas Habitability Scores as estimated by \pso.\\
    \footnotesize $\alpha$, $\beta$, $\gamma$ and $\delta$ record the parameters of Equation~\ref{eq:cdhscrs} in
    Table~\ref{tab:cdhscrs} and the parameters of Equation~\ref{eq:cdhsdrs} in Table~\ref{tab:cdhsdrs}. $Y_i$ and $Y_s$
    record the maxima for the objective functions. $i_i$ and $i_s$ specify the number of iterations taken to converge to
    a stable $\gbest$ value. Under the Class column there are four categories for the planets --- Psychroplanets (psy),
    Mesoplanets (mes), Non-Habitable planets (non) and Hypopsychroplanets (hyp).  $\mathit{CDHS}$ is the final score
    with $w_i=0.99$ and $w_s=0.01$.
  }
\end{table}

\begin{table}
  \centering
  \begin{subtable}{\textwidth}
    \centering
    \begin{tabular}{l r r r r r r r r r r}
      \toprule
      Name & Class & $r$ & $d$ & $t$ & $v$ & $e$ & $\rho$ & $\eta$ & $\mathit{CEESA}$ & $i$\\
      \midrule
      GJ 176 b & non & 0.304 & 0.001 & 0.375 & 0.271 & 0.050 & 0.467 & 0.808 & 1.52 &  85\\
      GJ 667 C b & non & 0.297 & 0.010 & 0.318 & 0.052 & 0.322 & 0.682 & 0.730 & 2.36 &  90\\
      GJ 667 C e & psy & 0.230 & 0.286 & 0.137 & 0.199 & 0.148 & 0.551 & 0.906 & 1.14 &  85\\
      GJ 667 C f & psy & 0.397 & 0.035 & 0.152 & 0.402 & 0.014 & 0.793 & 0.999 & 1.31 & 100\\
      GJ 3634 b & non & 0.178 & 0.175 & 0.005 & 0.194 & 0.447 & 0.894 & 0.657 & 2.07 &  94\\
      HD 20794 c & non & 0.073 & 0.142 & 0.452 & 0.190 & 0.144 & 0.953 & 0.635 & 1.20 &  78\\
      HD 40307 e & non & 0.156 & 0.307 & 0.185 & 0.033 & 0.319 & 0.428 & 0.939 & 2.69 &  88\\
      HD 40307 f & non & 0.272 & 0.231 & 0.064 & 0.305 & 0.127 & 0.676 & 0.802 & 1.28 &  77\\
      HD 40307 g & psy & 0.113 & 0.219 & 0.066 & 0.454 & 0.148 & 0.711 & 0.991 & 3.26 &  92\\
      Kepler-186 f & hyp & 0.039 & 0.159 & 0.116 & 0.329 & 0.357 & 0.253 & 0.919 & 1.35 &  70\\
      Proxima Cen b & psy & 0.272 & 0.173 & 0.284 & 0.193 & 0.079 & 0.615 & 0.114 & 0.99 &  75\\
      TRAPPIST-1 b & non & 0.488 & 0.151 & 0.039 & 0.193 & 0.129 & 0.151 & 0.014 & 0.99 &  87\\
      TRAPPIST-1 c & non & 0.172 & 0.236 & 0.275 & 0.242 & 0.075 & 0.969 & 0.962 & 1.06 &  80\\
      TRAPPIST-1 d & mes & 0.106 & 0.308 & 0.075 & 0.218 & 0.293 & 0.844 & 0.017 & 0.99 &  93\\
      TRAPPIST-1 e & psy & 0.189 & 0.266 & 0.192 & 0.094 & 0.260 & 0.371 & 0.006 & 0.99 &  84\\
      TRAPPIST-1 g & hyp & 0.326 & 0.186 & 0.143 & 0.278 & 0.067 & 0.315 & 0.021 & 1.00 &  76\\
      \bottomrule
    \end{tabular}
    \caption{Estimated habitability scores under DRS.}\label{tab:ceesadrs}
  \end{subtable}

  \vspace{4em}
